---
title: "Web data scraping with `rvest`"
description: "Learn how to extract valuable data from the web with ease and efficiency"
author:
  - name: Indira Puteri
    url: https://indiraputeri.github.io/
    orcid: 0009-0009-6959-6723
    affiliation: Student at Mathematical Science program, Faculty of Science, Universiti Brunei Darussalam and Statistics Lecturer at Universitas Islam Negeri Mataram, Indonesia
date: 02-05-2024
categories: [data, R, rvest, web-scraping] 
citation: 
  url: https://indiraputeri.github.io/posts/2024-03-29-post/ 
draft: false 
---

In today's data-centric era, accessing and analyzing online information has become crucial for businesses, researchers, and enthusiasts. However, manually retrieving data from websites is often tedious and ineffective. Enter web scraping -- a method that automates data extraction from web pages.

Among the top choices for web scraping in R is the `rvest` package. Created by Hadley Wickham, `rvest` offers an intuitive interface for navigating web pages, selecting HTML elements, and extracting desired data seamlessly.

With `rvest`, users can scrape various types of web data, including text, tables, images, and more. Whether gathering product prices from online stores, collating news headlines from media sites, or extracting weather forecasts, `rvest` streamlines the process with its user-friendly functions.

To begin using `rvest`, simply install the package from CRAN and load it into your R environment. From there, utilize functions like **`read_html`**, **`html_nodes`**, and **`html_text`** to retrieve HTML content, pinpoint specific elements via CSS selectors or XPath expressions, and extract the desired data.

For example, consider the task of scraping article titles from a news platform such as [detik.com](https://www.detik.com/). Using the **`rvest`** package, one can efficiently retrieve the HTML content of the page, pinpoint the CSS selector corresponding to the article titles, and extract the textual data. Within a short span, this approach yields a structured dataset composed of headlines, primed for further analysis. The code snippet below illustrates how to leverage **`rvest`**, in conjunction with the **`tidyverse`** package in R, to collect news titles from a website:

```{r}
#install.packages("rvest") 
library(rvest)

detik.com <- read_html("https://news.detik.com/") #Define/read the url

detik.com %>% html_nodes("h2.media__title") %>%  #point out the spesific node
  html_text() %>%                                #that represent the news title
  trimws()
```

Moreover, `rvest` seamlessly integrates with other R packages such as `dplyr` and `ggplot2`, and even `purrr` facilitating data manipulation, visualization, and analysis tasks. Whether constructing predictive models, conducting sentiment analysis, or crafting interactive dashboards, `rvest` complements your data science workflow effectively.

In the provided R script below, we utilize the **`rvest`** library to scrape web content from "news.detik.com", specifically targeting the **`<a>`** tags with the class attribute **`media__link`**. This is accomplished by selecting the appropriate nodes using **`html_nodes()`**. Following node selection, the **`map_df()`** function from the **`purrr`** package is employed to iterate over each node. Within this function, a small data frame is created for each node, where **`html_text()`** extracts the visible text of the link (i.e., the news title), and **`html_attr("href")`** retrieves the corresponding URL. The **`trimws()`** function is applied to clean up the extracted titles by removing any excess whitespace. The result is a tidy data frame, named **`news_data`**, containing columns for both the cleaned titles and their associated URLs, ready for further analysis or use in subsequent operations. This approach ensures a structured and efficient method for collecting web data, which can be crucial for tasks such as content aggregation, monitoring, or data analysis in digital journalism and other fields.

```{r}
library(purrr)
library(tibble)

# Define and read the URL
detik.com <- read_html("https://news.detik.com/")

# Extract news titles and their corresponding links
news_data <- detik.com %>%
  html_nodes("a.media__link") %>%
  map_df(~ tibble(
    title = html_text(.x) %>% trimws(), # Extract and trim the text
    link = html_attr(.x, "href")        # Extract the href attribute
  ))

# View the results
print(news_data)
```

In summary, `rvest` empowers R practitioners to leverage the abundance of web-based information and convert it into actionable insights. By automating web scraping, `rvest` enhances efficiency, boosts productivity, and opens up new avenues for data-driven decision-making. Whether you're a novice or a seasoned data scientist, `rvest` serves as a valuable asset for extracting knowledge from the web.
